Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.qmd
Removed best fit layouts

```{r}
#| label: best-fit-umap-tsne-pacamp
#| fig-cap: "Best fit for two C-shaped clusters data using UMAP (a1-a4) ($a_1$ = 0.09) and tSNE (b1-b4) ($a_1$ = 0.16) with the same number of non-empty bins ($m$ = 39). Both models show twist in $7\\text{-}D$ (a3, a4, b3, b4). Also, both NLDR methods are unable to accurately capture the width of the curvilinear clusters."
#| fig-width: 15
#| fig-height: 20
#| out-width: 90%

>>>>

```{r}
#| label: best-fit-umap-tsne-pacamp
#| fig-cap: "Best fit for two C-shaped clusters data using UMAP (a1-a4) ($a_1$ = 0.09) and tSNE (b1-b4) ($a_1$ = 0.16) with the same number of non-empty bins ($m$ = 39). Both models show twist in $7\\text{-}D$ (a3, a4, b3, b4). Also, both NLDR methods are unable to accurately capture the width of the curvilinear clusters."
#| fig-width: 15
#| fig-height: 20
#| out-width: 90%
#| eval: false
